%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{style/res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet}
\usepackage{hyperref}
\usepackage{etoolbox}
\usepackage{fancyhdr}
\usepackage{enumitem}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
%\lfoot{\hspace{-100pt} D. Hellfeld}
\lfoot{}
\cfoot{\hspace{-0.825in}\thepage}     % Adjust page number placement
\rfoot{}
\renewcommand{\headrulewidth}{0pt}

\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

%\def\labelitemi{$\diamond$}
%\def\labelitemi{$\cdot$}
%\def\labelitemi{-}
\def\labelitemi{$\circ$}

\setlength{\textwidth}{5.9in} % Text width of the document
\setlength{\sectionwidth}{1.2in}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME 
%----------------------------------------------------------------------------------------

\moveleft2.63\hoffset\centerline{\Large \bf{Daniel Hellfeld}} % Your name at the top
\vspace{-6pt}
\moveleft0.935\hoffset\vbox{\hrule width 7.115in height 0.8pt} % Horizontal line after name; adjust line thickness by changing the '1pt'
\vspace{-10pt}
\moveleft0.935\hoffset\vbox{\hrule width 7.115in height 0.5pt} % Horizontal line after name; adjust line thickness by changing the '1pt'

%----------------------------------------------------------------------------------------


\begin{resume}


%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\vspace{-10pt}
\section{\small{CONTACT}}  


Lawrence Berkeley National Laboratory \hfill 1.949.680.9345\\
1 Cyclotron Rd. (B50C - 3321C) \hfill \href{mailto:dhellfeld@berkeley.edu}{dhellfeld@berkeley.edu} $|$ \href{mailto:dhellfeld@lbl.gov} {dhellfeld@lbl.gov} \\
Berkeley, CA  94720  \hfill \href{https://dhellfeld.github.io}{dhellfeld.github.io} $|$ \href{https://www.linkedin.com/in/dhellfeld}{linkedin.com{\small{/}}in{\small{/}}dhellfeld} 

%4126 Etcheverry Hall \hfill 949.680.9345\\
%University of California, Berkeley \hfill \href{mailto:dhellfeld@berkeley.edu}{dhellfeld@berkeley.edu} $|$ \href{mailto:hellfeld1@llnl.gov} {hellfeld1@llnl.gov} \\
%Berkeley, CA  94720  \hfill \href{https://dhellfeld.github.io}{dhellfeld.github.io} $|$ \href{https://www.linkedin.com/in/dhellfeld}{linkedin.com/in/dhellfeld} 

%6402 Irwin Court \hfill 949.680.9345\\
%Apartment \# 3  \hfill \href{http://www.linkedin.com/in/danielhellfeld}{www.linkedin.com/in/danielhellfeld}  \\
%Oakland, CA 94609 \hfill \href{mailto:dhellfeld@berkeley.edu}{dhellfeld@berkeley.edu} $|$ \href{mailto:hellfeld1@llnl.gov} {hellfeld1@llnl.gov}

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{\small{OBJECTIVE}} 

To conduct scientific research in the field of nuclear engineering, specifically in the areas of radiation detection and nuclear nonproliferation.

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\small{EDUCATION}}

{\sl\bf Doctor of Philosophy (PhD),} Nuclear Engineering (4.0/4.0) \hfill {\bf Aug 2015 - Present}\\
{\sl University of California, Berkeley} \hfill {\sl Berkeley, CA}
\vspace{2.5pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt % Reduce space between items
\item Fellow at the Nuclear Science and Security Consortium (NSSC).
\item Area of current research: Coded aperture imaging of low-energy gamma-rays with CdZnTe detectors in both planar and spherical configurations.
%\item Thesis:~\emph{...}.
\item Advisor:~Kai Vetter.
\end{itemize}

{\sl\bf Master of Science (MS),} Nuclear Engineering (4.0/4.0) \hfill {\bf Aug 2013 - May 2015}\\
{\sl Texas A\&M University} \hfill {\sl College Station, TX}
\vspace{2.5pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt % Reduce space between items
\item Member of the Nuclear Security Science and Policy Institute (NSSPI).
\item Thesis:~\emph{Feasibility of Remote Nuclear Reactor Antineutrino Directionality via Elastic Electron Scattering in the WATer CHerenkov Monitor of ANtineutrinos (WATCHMAN)}.
\item Advisor:~Craig Marianno.
\end{itemize}

{\sl\bf Bachelor of Science (BS),} Physics (3.89/4.0) \hfill {\bf Sep 2009 - June 2013} \\
{\sl University of California, Santa Barbara} \hfill {\sl Santa Barbara, CA}
\vspace{2pt}

%----------------------------------------------------------------------------------------

 

%----------------------------------------------------------------------------------------
%	RESEARCH AND EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{\small{RESEARCH EXPERIENCE}}

{\sl\bf NSSC Graduate Research Fellow} \hfill {\bf Aug 2015 - Present} \\
{\sl Nuclear Science and Security Consortium} \hfill {\sl Berkeley, CA}\\
University of California, Berkeley
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Analyzing the coded aperture imaging performance of a spherical active coded aperture CdZnTe-based imaging system.
\item Optimized the coded configuration of detectors using simulations and iterative techniques.
\item Currently investigating the feasibility of real-time 3D imaging and scene data fusion as the system is moved freely through an environment.   
%Perform research in collaboration with UC Berkeley and Lawrence Berkeley National Laboratory in 
\end{itemize} 

{\sl\bf Graduate Student Intern} \hfill {\bf June 2015 - July 2015} \\
{\sl Lawrence Livermore National Laboratory} \hfill {\sl Livermore, CA}\\
Nuclear and Chemical Sciences Division, Rare Event Detection Group
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
%\item Performed Geant4 simulations and data analysis for the WATCHMAN project.
\item Investigated the impact of cosmogenic radionuclide backgrounds as a function of detector overburden and the effects on directional sensitivity.
\item Integrated reactor antineutrino-electron scattering event generator into the \href{https://github.com/rat-pac/rat-pac}{RAT-PAC} Geant4 simulation package.
%\item Completed and submitted a paper to a peer reviewed physics journal on nuclear reactor antineutrino directional sensitivity of water Cherenkov detectors.
\end{itemize} 

{\sl\bf NSSC Graduate Research Fellow} \hfill {\bf Nov 2014 - May 2015} \\
{\sl Nuclear Science and Security Consortium} \hfill {\sl Berkeley, CA}\\
University of California, Berkeley
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Analyzed antineutrino directional reconstruction and background suppression techniques.
\item Performed simulations and analysis of antineutrino scattering background sources in water.
%\item Performed master's thesis research on antineutrino detection for nuclear safeguards in collaboration with Lawrence Livermore National Laboratory.
\end{itemize} 
 
{\sl\bf Graduate Student Intern} \hfill {\bf June 2014 - Aug 2014} \\
{\sl Lawrence Livermore National Laboratory} \hfill {\sl Livermore, CA}\\
Nuclear and Chemical Sciences Division, Rare Event Detection Group
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Conducted Geant4 simulations and data analysis in ROOT for the proposed WATer CHerenkov Monitor of AntiNeutrinos (WATCHMAN) detector.
\item Studied the feasibility of nuclear reactor directionality using antineutrino-electron elastic scattering in WATCHMAN.
%\item Constructed an event generator in ROOT and incorporated the generator into two Geant4 simulations in order to simulate scattering events.
%\item Compared competing WATCHMAN simulation packages and presented findings in order to assist in the decision of which package should ultimately be used for the project.
\end{itemize}

{\sl\bf Graduate Research Assistant} \hfill {\bf Sep 2013 - Nov 2014} \\
{\sl Texas A\&M University} \hfill {\sl College Station, TX}\\
Department of Nuclear Engineering
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Investigated the use of silicon photodiodes to enhance scintillation detection capabilities.
\item Designed and constructed a multi-detector (NaI) housing for a vehicle-mounted radiation detection system.
%\item Constructed and characterized a mobile vehicle-based radiation detection system for wide area monitoring in urban environments.
%\item Performed various research tasks in the fields of nuclear security and radiation detection instrumentation development.
%\item Assisted in the teaching and grading associated with the graduate radiation detection laboratory course.
\end{itemize} 

%----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{\small{TEACHING EXPERIENCE}}

{\sl\bf Lab Instructor} \hfill {\bf Sep 2014 - Dec 2014} \\
{\sl Texas A\&M University} \hfill {\sl College Station, TX}\\
Department of Nuclear Engineering
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Responsible for the setup and teardown of weekly laboratory experiments for the graduate radiation detection course, NUEN 605.
\item Assisted students with lab procedures and answered any questions regarding experiments or course content.
%\item Responsible for weekly lab report grading.
\end{itemize} 

%{\sl\bf Lab Instructor/Grader} \hfill {\bf Sep 2014 - Dec 2014} \\
%{\sl Texas A\&M University} \hfill {\sl College Station, TX}\\
%Department of Nuclear Engineering
%\vspace{2pt}
%\begin{itemize}[leftmargin=4ex] \itemsep -2pt
%\item Responsible for the setup and teardown of weekly laboratory experiments for the graduate radiation detection course, NUEN 605.
%\item Assisted students with lab procedures and answered any questions regarding experiments or course content.
%\item Responsible for weekly lab report grading.
%\end{itemize} 

{\sl\bf Math/Physics Tutor} \hfill {\bf Jan 2013 - Mar 2013} \\
{\sl Campus Learning and Assistance Services} \hfill {\sl Santa Barbara, CA}\\
University of California, Santa Barbara
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Tutored UCSB's Astronomy 1: Introduction to Astronomy. 		
\item Instructed four 50-minute sessions a week with $\sim$20 students each.
\item Reviewed confusing concepts, prepared example problems and study sheets, and answered any individual questions.
%\item Held two additional office hours a week open to any math or physics questions. 
\end{itemize} 

%----------------------------------------------------------------------------------------





%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\small{SCIENTIFIC COMPUTING \\ SKILLS}}

{\sl\bf Languages:} \hfill Python, C\verb!++!, bash\\
{\sl\bf Mathematical/Analysis Software:} \hfill ROOT, Mathematica, Matlab\\ %Octave
%{\sl\bf Databases:} \hfill SQL\\
{\sl\bf Monte Carlo Particle Transport Software:} \hfill Geant4, MCNP5/MCNPX, Serpent\\
{\sl\bf Gamma Spectroscopy Software:} \hfill GENIE-2000, MAESTRO\\
{\sl\bf Nuclear Burnup Software:} \hfill ORIGEN2, CINDER-90, TransLAT\\
{\sl\bf Build Systems:} \hfill make, CMake\\
{\sl\bf Operating Systems:} \hfill Mac, Linux, MS Windows\\
{\sl\bf Documentation:} \hfill Doxygen, Sphinx\\
{\sl\bf Version Control:} \hfill git\\
%{\sl\bf IDEs:} \hfill Xcode\\
%{\sl\bf Text Editors:} \hfill Emacs, Sublime, Nano, Text Wrangler\\
{\sl\bf Other Software:} \hfill \LaTeX, MS Office

%----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------
%	SOCIETY SECTION
%----------------------------------------------------------------------------------------

\section{\small{PROFESSIONAL SOCIETY MEMBERSHIPS}}

IEEE Nuclear and Plasma Sciences Society \hfill  {\bf 2016 - Present}\\
Institute of Nuclear Materials Management \hfill  {\bf 2014 - Present}\\
American Nuclear Society \hfill {\bf 2013 - Present}\\
National Society of Collegiate Scholars \hfill  {\bf 2009 - 2013}\\
Golden Key International Honor Society \hfill  {\bf 2009 - 2013}

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{\small{AWARDS}}

{\bf Nuclear Science and Security Consortium Fellowship}, UC Berkeley \hfill {\bf Aug 2015}\\
{\bf JD Williams Best Poster Award}, INMM 56\textsuperscript{th} Annual Meeting \hfill {\bf July 2015}\\
{\bf Nuclear Science and Security Consortium Fellowship}, UC Berkeley \hfill {\bf Nov 2014}\\
{\bf Graduate Enhancement Fellowship}, Texas A\&M University \hfill {\bf Aug 2013}\\
{\bf Highest Academic Honor Award}, UC Santa Barbara, Physics Dept. \hfill {\bf May 2013}\\
{\bf Highest Honors}, UC Santa Barbara \hfill {\bf May 2013}

%{\bf Dean's Honor List}, UC Santa Barbara, 10 quarters \hfill {\bf 2009 - 2013}

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	WORKSHOPS SECTION
%----------------------------------------------------------------------------------------

\section{\small{WORKSHOPS\newline \& SEMINARS}}

%{\bf School of Nukes} \hfill {\bf June 2017}\\
%{\small{Los Alamos National Laboratory}} \hfill {\sl Los Alamos, NM}\\[-3.5ex]

{\bf Fukushima Fieldwork for Radiation Disaster Recovery} \hfill {\bf Aug 2016}\\
{\small{Phoenix Program, Hiroshima University}} \hfill {\sl Fukushima, Japan}\\[-3.5ex]

{\bf Python Boot Camp} \hfill {\bf Aug 2016}\\
{\small{UC Berkeley, NSF, Berkeley Institute for Data Science}} \hfill {\sl Berkeley, CA}\\[-3.5ex]

\newpage
{\bf Nuclear Safeguards Policy and Information Analysis Course} \hfill {\bf June 2016}\\
{\small{Middlebury Institute for International Studies at Monterey}} \hfill {\sl Monterey, CA}\\[-3.5ex]

{\bf Next Generation Fukushima Workshop} \hfill {\bf Apr 2016}\\
{\small{IRC, LBNL, FREA, Koriyama City}} \hfill {\sl Koriyama, Japan}\\[-3.5ex]

{\bf International Symposium for Resilient Communities} \hfill {\bf Apr 2016}\\
{\small{IRC, LBNL, FREA, Koriyama City}} \hfill {\sl Koriyama, Japan}\\[-3.5ex]

{\bf Applied Antineutrino Physics Workshop} \hfill {\bf Dec 2015}\\
{\small{Center for Neutrino Physics, Virginia Tech University}} \hfill {\sl Arlington, CA}\\[-3.5ex]

{\bf Public Policy and Nuclear Threats Summer Boot Camp} \hfill {\bf June 2015}\\
{\small{Institute on Global Conflict and Cooperation, UC San Diego}} \hfill {\sl San Diego, CA}\\[-3.5ex]

{\bf Global Nuclear HR Development for Safety, Security \& Safeguards} \hfill {\bf Feb 2015}\\
{\small{Academy for Global Nuclear Safety and Security Agent, Tokyo Tech}}  \hfill {\sl Tokyo, Japan}\\[-3.5ex]
%{\bf Nuclear Safety in the Post-Fukushima Era} \hfill {\bf Feb 2015}\\
%{Tokyo Institute of Technology}  \hfill {\sl Tokyo, Japan}

{\bf NDA Fundamentals for Nuclear Safeguards}   \hfill {\bf Nov 2014}\\
{\small{Next Generation Safeguards Initiative, Oak Ridge National Laboratory}} \hfill  {\sl Oak Ridge, TN}

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{\small{CERTIFICATIONS}}

%{\bf General Radiation Safety Training}  \hfill {\bf Feb 2014}\\
%{Environmental Health and Safety Office, Texas A\&M University} \hfill {\sl College Station, TX}


%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	CONFERENCES SECTION
%----------------------------------------------------------------------------------------

\section{\small{CONFERENCE PROCEEDINGS}}

 \begin{thebibliography}{3}
 \raggedright
 \vspace{10pt}

% \bibitem{1} \textbf{D.~Hellfeld}, P.~Barton, R.~Barnowski, A.~Haefner, D.~Gunter, L.~Mihailescu, K.~Vetter, ``Handheld Volumetric Imaging with PRISM", in Proc. IEEE NSS/MIC, Atlanta, Georgia, 2017. Oral presentation.
 
 \bibitem{1} \textbf{D.~Hellfeld}, P.~Barton, D.~Gunter, L.~Mihailescu, K.~Vetter, ``Optimization of a Spherical Active Coded Mask Imager", in Proc. IEEE NSS/MIC, Strasbourg, France, 2016. Oral presentation.
 
 \bibitem{1} \textbf{D.~Hellfeld}, A.~Bernstein, S.~Dazeley, C.~Marianno, ``Directional Reconstruction of Reactor Antineutrinos via Electron Scattering in Gd-doped Water Cherenkov Detectors", in Proc. IEEE NSS/MIC, Strasbourg, France, 2016. Poster presentation.
 
 \bibitem{1} \textbf{D.~Hellfeld}, A.~Bernstein, S.~Dazeley, C.~Marianno, ``Nuclear Reactor Antineutrino Directionality via Elastic Electron Scattering in a Gd-Doped Water Cherenkov Detector", in Proc. INMM Annual Meeting, Indian Wells, CA, 2015. Poster presentation.

 \end{thebibliography}

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\small{PUBLICATIONS \\\& PAPERS}}

\begin{thebibliography}{3}
 \raggedright
\vspace{10pt}

\bibitem{1} \textbf{D.~Hellfeld}, P.~Barton, D.~Gunter, L.~Mihailescu, K.~Vetter, ``A Spherical Active Coded Aperture for 4$\pi$ Gamma-ray Imaging", \href{http://www.google.com}{Submitting to IEEE Trans. Nucl. Sci. (2017)}.
 
\bibitem{1} \textbf{D.~Hellfeld}, S.~Dazeley, A.~Bernstein, C.~Marianno, ``Reconstructing the Direction of Reactor Antineutrinos via Electron Scattering in Gd-Doped Water Cherenkov Detectors", \href{http://www.sciencedirect.com/science/article/pii/S0168900216310555}{Nucl. Instrum. Methods A, 841 (2017) 130-138}.

\bibitem{2} N.~S.~Bowden, K.~M.~Heeger, P.~Huber, C.~Mariani, R.~B.~Vogelaar. ``Applied Antineutrino Physics 2015 - Conference Summary". \href{http://arxiv.org/abs/1602.04759}{arXiv:1602.04759} (2015).

\bibitem{3} \textbf{D.~Hellfeld}, C.~Marianno, W.~Charlton, R.~Webb, ``Feasibility of Nuclear Reactor Antineutrino Directionality via Elastic Electron Scattering in the WATer CHerenkov Monitor of ANtineutrinos (WATCHMAN)", \href{http://hdl.handle.net/1969.1/155140}{Master's Thesis}, Texas A\&M University, 2015.

\bibitem{4} M.~Askins, M.~Bergevin, A.~Bernstein, S.~Dazeley, S.~T.~Dye, T.~Handler, A.~Hatzikoutelis, \textbf{D.~Hellfeld}, P.~Jaffke, Y.~Kamyshkov, B.~J.~Land, J.~G.~Learned, P.~Marleau, C.~Mauger, G.~D.~Orebi Gann, C.~Roecker, S.~D.~Rountree, T.~M.~Shokair, M.~B.~Smy, R.~Svoboda, M.~Sweany, M.~R.~Vagins, K.~A.~van Bibber, R.~B.~Vogelaar, M.~J.~Wetstein, M.~Yeh, ``The Physics and Nuclear Nonproliferation Goals of WATCHMAN: A WATer CHerenkov Monitor for ANtineutrinos", \href{http://arxiv.org/pdf/1502.01132.pdf}{arXiv:1502.01132} (2015).

\end{thebibliography}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	RELEVANT COURSEWORK SECTION
%----------------------------------------------------------------------------------------

\section{\small{RELEVANT COURSEWORK}}

\textbf{University of California, Berkeley}\\[-2.3ex]
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Nuclear Security: The Nexus Between Policy and Technology ({\footnotesize{NE 285}}) [\emph{in progess}]
\item Numerical Simulation in Radiation Transport ({\footnotesize{NE 255}})
\item Medical Imaging  Signals and Systems ({\footnotesize{BIOENG/ELENG 261}})
\item Teaching Techniques in Nuclear Engineering ({\footnotesize{NE 375}})
\item Analytical Methods for Nonproliferation ({\footnotesize{NE 230}})
\item Nuclear Physics ({\footnotesize{NE 201}})
%\item Introduction to Nuclear Reactor Theory (NE150)
\item Nuclear Reactor Theory ({\footnotesize{NE 250}})
\item Nuclear Reactions and Radiation ({\footnotesize{NE 101}})
\item Nuclear Materials ({\footnotesize{NE 120}})
%\item Advanced Concepts in Radiation Detection and Measurement (NE204)  [\emph{in progess}]
%\item Charged Particle Source and Beam Technology (NE282)
%\item Special Topics (NE290)
\end{itemize}

\textbf{Texas A\&M University}\\[-2.3ex]
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Radiation Interactions and Shielding ({\footnotesize{NUEN 604}})
\item Radiation Detection and Nuclear Materials Measurement ({\footnotesize{NUEN 605}})
\item Reactor Theory ({\footnotesize{NUEN 601}})
\item Nuclear Fuel Cycles and Nuclear Materials Safeguards ({\footnotesize{NUEN 651}})
\item Nuclear Reactor Analysis and Experimentation ({\footnotesize{NUEN 606}})
\item Nuclear Nonproliferation and Arms Control ({\footnotesize{NUEN 650}})
\item Monte Carlo Computational Particle Transport ({\footnotesize{NUEN 630}})
\item Special Topics: Introduction to Geant4 Monte Carlo Transport ({\footnotesize{NUEN 689}})
\item Statistical Analysis ({\footnotesize{STAT 601}})
\end{itemize}

\textbf{University of California, Santa Barbara}\\[-2.3ex]
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Classical Mechanics ({\footnotesize{PHYS 105A/B}}) 
\item Electromagnetism ({\footnotesize{PHYS 110A/B}}) 
\item Quantum Mechanics ({\footnotesize{PHYS 115A/B/C}}) 
\item Nuclear Physics ({\footnotesize{PHYS 150}}) 
\item Mathematical Methods for Theoretical Physics ({\footnotesize{PHYS 100A/B}}) 
\item Thermodynamic and Statistical Physics ({\footnotesize{PHYS 119A}}) 
\item Particle Physics ({\footnotesize{PHYS 125}}) 
\item Astronomy/Cosmology ({\footnotesize{ASTRO1/2}})
\item Analog Electronics ({\footnotesize{PHYS 127AL}}) 
\item Advanced Physics Laboratory ({\footnotesize{PHYS 128AL/BL}}) 
\item California Physics ({\footnotesize{PHYS 120}})
\item Differential Equations and Linear Algebra ({\footnotesize{MATH 3C/5A}}) 
\item Vector Calculus ({\footnotesize{MATH 5B/C}}) 
\end{itemize}

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------

\section{\small{REFERENCES}}

{\sl Available upon request}.

%{\bf Prof.\,Kai Vetter} \\
%{\sl Head, Professor-in-Residence} \\
%Applied Nuclear Physics, Lawrence Berkeley National Laboratory, Livermore, CA \\
%Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA \\
%\href{mailto:kvetter@berkeley.edu}{kvetter@berkeley.edu} $|$ xxx.xxx.xxxx
%
%{\bf Dr.\,Steven Dazeley} \\
%{\sl Staff Scientist} \\
%Lawrence Livermore National Laboratory, Livermore, CA \\
%Nuclear and Chemical Sciences Division, Rare Event Detection Group \\
%\href{mailto:dazeley2@llnl.gov}{dazeley2@llnl.gov} $|$ 925.423.4792
%
%{\bf Prof.\,Craig Marianno} \\
%{\sl Assistant Professor, Senior Research Engineer} \\
%Department of Nuclear Engineering, Texas A\&M University, College Station, TX \\
%Nuclear Security Science and Policy Institute (NSSPI) \\
%\href{mailto:marianno@tamu.edu}{marianno@tamu.edu} $|$ 979.845.6093



%----------------------------------------------------------------------------------------


\end{resume}
\end{document}