\section{\small{CONFERENCE PROCEEDINGS}}

 \begin{thebibliography}{3}
 \raggedright
 \vspace{10pt}
 
%\bibitem{1} A.~Haefner, R.~Barnowski, P.~Barton, \textbf{D.~Hellfeld}, T.~Joshi, R.~Pavlovsky, Y.~Sanada, Y.~Shikaze, T.~Torii, K.~Vetter, ``3-D Radiation Mapping and Data Fusion for Environmental Remediation and Cleanup", \href{http://www.wmsym.org/}{\emph{in Proc. Waste Management Symp.}}, Phoenix, AZ, Mar. 2018.

%\bibitem{1} K.~Vetter, A.~Haefner, R.~Barnowski, \textbf{D.~Hellfeld}, P.~Barton, L.~Mihailescu, R.~Pavlovsky ``Gamma-Ray Imaging and Sensor Fusion: Gamma-Ray Vision in 3D and Color", \href{http://ewh.ieee.org/soc/nps/nss-mic/2017/News.html}{\emph{in Proc. IEEE NSS-MIC}}, Atlanta, GA, Oct. 2017.

\bibitem{1} \textbf{D.~Hellfeld}, P.~Barton, A.~Haefner, D.~Gunter, L.~Mihailescu, K.~Vetter, ``Omnidirectional 3D Gamma-ray Imaging with a Free-moving Spherical Active Coded Aperture", \href{http://ewh.ieee.org/soc/nps/nss-mic/2017/News.html}{\emph{in Proc. IEEE NSS-MIC}}, Atlanta, GA, Oct. 2017.

%\bibitem{1} P.~Barton, M.~Turqueti, A.~Haefner, R.~Barnowski, \textbf{D.~Hellfeld}, V.~Negut, L.~Mihailescu, K.~Vetter, ``PRISM - A CZT-Based Portable Radiation Imaging Spectroscopy and Mapping System", \href{http://ewh.ieee.org/soc/nps/nss-mic/2017/News.html}{\emph{in Proc. IEEE NSS-MIC}}, Atlanta, GA, Oct. 2017. 

 \bibitem{1} S.~Dazeley, A.~Bernstein, T.~Classen, E.~Reedy, \textbf{D.~Hellfeld}, M.~Duvall, C.~Marianno, ``Antineutrino Detection based on \textsuperscript{6}Li-doped Pulse Shape Sensitive Plastic Scintillator and Gd-doped Water", \href{http://www.creteconf.org/index.html}{\emph{in Proc. Int. Conf. on the App. of Nucl. Tech.}}, Crete, Greece, Jun. 2017. 
 
 \bibitem{1} \textbf{D.~Hellfeld}, P.~Barton, D.~Gunter, L.~Mihailescu, K.~Vetter, ``Optimization of a Spherical Active Coded Mask Imager", \href{http://ieeexplore.ieee.org/document/8069853/}{\emph{in Proc. IEEE NSS-MIC}}, Strasbourg, France, Nov. 2016. 
 
 \bibitem{1} \textbf{D.~Hellfeld}, A.~Bernstein, S.~Dazeley, C.~Marianno, ``Nuclear Reactor Antineutrino Directionality via Elastic Electron Scattering in a Gd-Doped Water Cherenkov Detector", \href{https://www.inmm.org/INMM-Resources/Proceedings-Presentations/Annual-Meeting-Proceedings}{\emph{in Proc. INMM Annual Meeting}}, Indian Wells, CA, Jul. 2015. 
 
 \end{thebibliography}
