\section{\small{PUBLICATIONS \\\& PAPERS}}

\begin{thebibliography}{3}
 \raggedright
\vspace{10pt}

\bibitem{1} \textbf{D.~Hellfeld}, P.~Barton, D.~Gunter, L.~Mihailescu, K.~Vetter, ``A Spherical Active Coded Aperture for 4$\pi$ Gamma-ray Imaging", \href{http://ieeexplore.ieee.org/document/8048531/}{\emph{IEEE Trans. Nucl. Sci.}}, vol.~64, no.~11, pp.~1-6, 2017.
 
\bibitem{1} \textbf{D.~Hellfeld}, S.~Dazeley, A.~Bernstein, C.~Marianno, ``Reconstructing the Direction of Reactor Antineutrinos via Electron Scattering in Gd-Doped Water Cherenkov Detectors", \href{http://www.sciencedirect.com/science/article/pii/S0168900216310555}{\emph{Nucl. Instrum. Methods A}}, vol.~841, pp.~130-138, 2017.

\bibitem{2} N.~S.~Bowden, K.~M.~Heeger, P.~Huber, C.~Mariani, R.~B.~Vogelaar. ``Applied Antineutrino Physics 2015 - Conference Summary". \href{http://arxiv.org/abs/1602.04759}{arXiv:1602.04759}, 2015.

\bibitem{3} \textbf{D.~Hellfeld}, C.~Marianno, W.~Charlton, R.~Webb, ``Feasibility of Nuclear Reactor Antineutrino Directionality via Elastic Electron Scattering in the WATer CHerenkov Monitor of ANtineutrinos (WATCHMAN)", \href{http://hdl.handle.net/1969.1/155140}{\emph{Master's Thesis}}, Texas A\&M University, 2015.

\bibitem{4} M.~Askins, M.~Bergevin, A.~Bernstein, S.~Dazeley, S.~T.~Dye, T.~Handler, A.~Hatzikoutelis, \textbf{D.~Hellfeld}, P.~Jaffke, Y.~Kamyshkov, B.~J.~Land, J.~G.~Learned, P.~Marleau, C.~Mauger, G.~D.~Orebi Gann, C.~Roecker, S.~D.~Rountree, T.~M.~Shokair, M.~B.~Smy, R.~Svoboda, M.~Sweany, M.~R.~Vagins, K.~A.~van Bibber, R.~B.~Vogelaar, M.~J.~Wetstein, M.~Yeh, ``The Physics and Nuclear Nonproliferation Goals of WATCHMAN: A WATer CHerenkov Monitor for ANtineutrinos", \href{http://arxiv.org/pdf/1502.01132.pdf}{arXiv:1502.01132}, 2015.

\end{thebibliography}