\section{\small{TEACHING EXPERIENCE}}

{\sl\bf Lecturer} \hfill {\bf Jan 2018 - May 2018} \\
{\sl Department of Nuclear Engineering}, UC Berkeley \hfill {\sl Berkeley, CA}\\[-2.8ex]
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Gave multiple lectures for the undergraduate radiation detection course, NE 104.
\item Semiconductor (Si/Ge) detector operation, manufacturing, signal generation, and applications.
\item Alternative semiconductor materials and advanced readout schemes.
\item Scintillation detection principles, readout techniques, and limitations.
\end{itemize} 

{\sl\bf Lab Instructor} \hfill {\bf Sep 2014 - Dec 2014} \\
{\sl Department of Nuclear Engineering}, Texas A\&M University \hfill {\sl College Station, TX}\\[-2.8ex]
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Responsible for the setup and teardown of weekly laboratory experiments for the graduate radiation detection course, NUEN 605.
\item Assisted students with lab procedures and answered any questions regarding experiments or course content.
%\item Responsible for weekly lab report grading.
\end{itemize} 

{\sl\bf Math/Physics Tutor} \hfill {\bf Jan 2013 - Mar 2013} \\
{\sl Campus Learning and Assistance Services}, UC Santa Barbara \hfill {\sl Santa Barbara, CA} \\[-2.8ex]
\vspace{2pt}
\begin{itemize}[leftmargin=4ex] \itemsep -2pt
\item Tutored UCSB's Astronomy 1: Introduction to Astronomy. 		
%\item Instructed four 50-minute sessions a week with 20 students each.
\item Reviewed confusing concepts, prepared example problems and study guides, and answered any individual questions.
%\item Held two additional office hours a week open to any math or physics questions. 
\end{itemize} 