\section{\small{POSTERS}}

\vspace{10pt}
\begin{enumerate}[label={[\arabic*]}, leftmargin=*, labelsep=10pt, align=left]
    \item ADD AUTHORS, ``Experimental Demonstration of Additive Point Source Localization", \emph{IEEE NSS-MIC}, Manchester, United Kingdom, Nov.~2019.
    \item ADD AUTHORS, ``Contextual Sensing for Mobile Urban Radiological Search", \emph{IEEE NSS-MIC}, Manchester, United Kingdom, Nov.~2019.
    \item ADD AUTHORS, ``Coded-Aperture Imaging using the Polaris-LAMP Platform", \emph{IEEE NSS-MIC}, Manchester, United Kingdom, Nov.~2019.
    \item ADD AUTHORS, ``Additive Point Source Localization", \emph{IEEE NSS-MIC}, Sydney, Australia, Nov.~2018.
    \item ADD AUTHORS, ``Portable Radiation Imaging, Spectroscopy and Mapping (PRISM) System", \emph{Special Operations Nexus Summit}, Tampa, FL, Jul.~2018.
    \item ADD AUTHORS, ``Near-field 3D Spherical Active Coded Aperture Gamma-ray Imaging", \emph{SORMA}, Ann Arbor, MI, Jun.~2018.
    \item ADD AUTHORS, ``3D Gamma-ray Imaging and Scene Data Fusion", \emph{NSSC Program Review}, Berkeley, CA, Sep.~2017.
    \item ADD AUTHORS, ``3D Handheld Mapping of Radioactive Sources for International Nuclear Safeguards", \emph{Novel Technologies, Techniques, and Methods for Safeguards and Arms Control Verification Workshop}, Albuquerque, NM, Aug.~2017.
    \item ADD AUTHORS, ``Directional Reconstruction of Reactor Antineutrinos via Electron Scattering in Gd-doped Water Cherenkov Detectors", \emph{IEEE NSS-MIC}, Strasbourg, France, Nov.~2016.
    \item ADD AUTHORS, ``Coded Aperture Gamma-Ray Imaging in Planar and Spherical Configurations", \emph{SORMA West}, Berkeley, CA, May~2016.
    \item ADD AUTHORS, ``Towards 3D Gamma Ray Vision with HEMI and Looking Forward with PRISM", \emph{Next Generation Fukushima Workshop}, Koriyama, Japan, Apr.~2016.
    \item ADD AUTHORS, ``Nuclear Reactor Antineutrino Directionality via Elastic Electron Scattering in a Gd-Doped Water Cherenkov Detector", \emph{INMM Annual Meeting}, Indian Wells, CA, Jul.~2015.
\end{enumerate}
