\section{\small{TALKS}}

\vspace{10pt}
\begin{enumerate}[label={[\arabic*]}, leftmargin=*, labelsep=10pt, align=left]
    \item ``Gamma-ray Point-source Localization and Sparse Image Reconstruction using Poisson Likelihood", \emph{LBNL NSD Staff Meeting}, Berkeley, CA, Apr.~2019.
    \item ``Real-time Free-moving Volumetric Coded Aperture Gamma-ray Imaging in PRISM", \emph{IEEE NSS-MIC}, Sydney, Australia, Nov.~2018.
    \item ``MiniPRISM: A Compact Gamma-ray Imaging System for 3D Real-Time Localization and Mapping onboard an Unmanned Aerial System", \emph{IEEE NSS-MIC}, Sydney, Australia, Nov.~2018.
    \item ``Free-moving 3D Coded Aperture Gamma-ray Imaging and Scene Data Fusion", \emph{UPR Meeting}, Ann Arbor, MI, Jun.~2018.
    \item ``Omnidirectional Volumetric Coded Aperture Gamma-ray Imaging", \emph{LBNL NSD Staff Meeting}, Berkeley, CA, Jan.~2018.
    \item ``Volumetric Coded Aperture Gamma-ray Imaging with PRISM", \emph{NSSC Schubert Review, Berkeley}, CA, Dec.~2017.
    \item ``Omnidirectional 3D Gamma-ray Imaging with a Free-moving Spherical Active Coded Aperture", \emph{IEEE NSS-MIC}, Atlanta, Georgia, Oct.~2017.
    \item ``Radiological Source Localization with an Omnidirectional Spherical Active Coded Aperture", \emph{UPR Meeting}, Walnut Creek, CA, Jun.~2017.
    \item ``Optimization of a Spherical Active Coded Mask Imager", \emph{IEEE NSS-MIC}, Strasbourg, France, Nov.~2016.
    \item \hspace{-5pt}``Reactor Antineutrino Directionality via Elastic Electron Scattering in Gd-Doped Water Cherenkov Detectors", \emph{Applied Antineutrino Physics Workshop}, Arlington, VA, Dec.~2015.
\end{enumerate}
